Imputation of Incomplete Multilevel Data with \proglang{R}

### 2023-10-27 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
fix analysis after imputation case study 2

The analysis model for this dataset is a prediction model with `mort` as the outcome. In this tutorial we'll estimate the adjusted prognostic effect of `ct` on mortality outcomes. The estimand is the adjusted odds ratio for `ct`, after including `type`, `age` `motor_score` and `pupil` into the analysis model: 
```{r mod}
mod <- mort ~ 1 + type + age + motor_score + pupil + ct + (1 | name) 
```

@@

The estimated effects in the complete data are presented in Table XYZ.

@@

```{r forest, echo=FALSE}
# fits <-
#   purrr::map_dfr(
#     unique(impact$name),
#     ~ {
#       glm(
#         mort ~ 1 + age + motor_score + pupil + ct,
#         family = "binomial",
#         data = filter(impact, name == .x)
#       )
#     } %>%
#       broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>%
#       .[, c("term", "estimate", "conf.low", "conf.high")] %>%
#       cbind(name = as.character(.x), .)
#   ) %>% filter(term %in% c("ctIII", "ctIV/V"))
# 
# n <- impact %>% group_by(name) %>% 
#   tally()
# 
# fits %>% left_join(n, by = "name") %>% 
#   ggplot(aes(y = name, x = estimate, color = term, linewidth = n)) +
#   geom_vline(xintercept = 1, linewidth = 1.5, color = "grey95") +
#   geom_linerange(aes(y = name, xmin = conf.low, xmax = conf.high, linewidth = 0.5), position = position_dodge(width = 0.5)) +
#   geom_point(shape = 20, position = position_dodge(width = 0.5)) +
#   labs(y = "Study", x = "Adjusted odds ratio for ct", color = NULL) +
#   theme_classic() +
#   scale_size(guide = 'none')
# # TODO: add heterogeneity in distribution of ct -> prevalence in ct across clusters with CI
# # TODO: missingness prop inside clusters
# # TODO: make row height proportional to pattern frequency
```
<!-- We will use the following estimates as comparative truth in this tutorial: -->
```{r truth}
# fit <- glmer(mod, family = "binomial", data = impact) # fit the model
# tidy(fit, conf.int = TRUE, exponentiate = TRUE)       # print estimates
```

@@

This shows us that `hypox` and `hypot` would not be useful auxiliary variables for imputing `ct`. Depending on the minimum required correlation, `tsah` could be useful, while `edh` has the strongest correlation with `ct` out of all the variables in the data and should definitely be included in the imputation model. For the imputation of `pupil`, none of the potential auxiliary variables has a very strong relation, but `hypots` could be used. We conclude that we can exclude `hypox` from the data, since this is neither an analysis model variable nor an auxiliary variable for imputation:
```{r}
dat <- select(dat, !hypox)  # remove variable
```

@@

Analyze the imputed data:
```{r impact-fit, cache=TRUE}
fit <- imp %>% 
  with(glmer(mort ~ type + age + as.factor(motor_score) + pupil + ct + (1 | name), family = "binomial")) 
tidy(pool(fit))
as.mitml.result(fit)
# testEstimates(as.mitml.result(fit))
```

>>>>

The analysis model for this dataset is a prediction model with `mort` as the outcome. In this tutorial we'll estimate the adjusted prognostic effect of `ct` on mortality outcomes. The estimand is the adjusted odds ratio for `ct`, after including `type`, `age` `motor_score` and `pupil` into the analysis model: 
```{r mod}
mod <- mort ~ type + age + motor_score + pupil + ct + (1 | name) 
```

@@

@@

```{r forest, echo=FALSE}
# fits <-
#   purrr::map_dfr(
#     unique(impact$name),
#     ~ {
#       glm(
#         mort ~ 1 + age + motor_score + pupil + ct,
#         family = "binomial",
#         data = filter(impact, name == .x)
#       )
#     } %>%
#       broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>%
#       .[, c("term", "estimate", "conf.low", "conf.high")] %>%
#       cbind(name = as.character(.x), .)
#   ) %>% filter(term %in% c("ctIII", "ctIV/V"))
# 
# n <- impact %>% group_by(name) %>% 
#   tally()
# 
# fits %>% left_join(n, by = "name") %>% 
#   ggplot(aes(y = name, x = estimate, color = term, linewidth = n)) +
#   geom_vline(xintercept = 1, linewidth = 1.5, color = "grey95") +
#   geom_linerange(aes(y = name, xmin = conf.low, xmax = conf.high, linewidth = 0.5), position = position_dodge(width = 0.5)) +
#   geom_point(shape = 20, position = position_dodge(width = 0.5)) +
#   labs(y = "Study", x = "Adjusted odds ratio for ct", color = NULL) +
#   theme_classic() +
#   scale_size(guide = 'none')
# # TODO: add heterogeneity in distribution of ct -> prevalence in ct across clusters with CI
# # TODO: missingness prop inside clusters
# # TODO: make row height proportional to pattern frequency
```

We will use the complete data estimates as comparative truth in this tutorial. The estimated effects in the complete data are presented in Table XYZ. 
```{r impact_truth, include=FALSE, echo=TRUE}
fit <- glmer(mod, family = "binomial", data = impact) # fit the model
tidy(fit, conf.int = TRUE, exponentiate = TRUE)       # print estimates
```

@@

This shows us that `hypox` and `hypot` would not be useful auxiliary variables for imputing `ct`. Depending on the minimum required correlation, `tsah` could be useful, while `edh` has the strongest correlation with `ct` out of all the variables in the data and should definitely be included in the imputation model. For the imputation of `pupil`, none of the potential auxiliary variables has a very strong relation, but `hypots` could be used. We conclude that we can exclude `hypox` from the data, since this is neither an analysis model variable nor an auxiliary variable for imputation:
```{r}
dat <- select(dat, !hypox)  # remove variable
dat <- mutate(dat, motor_score = as.factor(motor_score))
```

@@

Analyze the imputed data:
```{r impact-fit, cache=TRUE}
fit <- imp %>% 
  with(glmer(
    mort ~ type + age + as.factor(motor_score) + pupil + ct + (1 | name),
    family = "binomial"
    )) 
# tidy(pool(fit))
# as.mitml.result(fit)
# testEstimates(as.mitml.result(fit))
```
The estimated effects after imputation are presented in Table XYZ.
